---
title: "Tutorial"
author: "Michał Kuć"
date: "2024-04-15"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Lab2)
```

# Introduction

Recombination chambers are an unpopular type of ionisation chamber. They are based on an initial ion recombination phenomenon that allows the quality of the radiation field measurement to be determined.
An example article containing information about recombination chambers is available at: [Zielczyński, 2008](https://bibliotekanauki.pl/articles/147680.pdf)
Recombination chambers:

|Chamber type| REM-2 | F1 | T5 | GW2 |
|---|:-:|:-:|:-:|:-:|
| Electrodes | TE* | TE* | TE* | Al |
| Gas | CH4+N2 | C2H6 | C2H6 | CO2|
| Application | Radiation protection | Beam | Beam | Radiation protection |

\* Tissue Equivalent

# Functions

The project includes

 * function that generates an ion collection efficiency function
 * function that determines the recombination voltage value
 * function that creates the sample measurement data from .xlsx file

## f(u) characteristic
f(u) characteristic is current-voltage I(U) characteristic normalized to the saturation condition I(Us)

```{r fu}
characteristic <- recombination_characteristic(seq(10, 1000, by = 10), L=4)
attributes(characteristic)
plot(characteristic$voltage , characteristic$current)

```

## Ur calculator

Calculation of the recombination voltage for previously determined f(u) characteristic

```{r Ur}
recombination_voltage <- calculate_recombination_voltage(characteristic, r = 0.96)
attributes(recombination_voltage)
```

## Read the measurement data


```{r dataset_read}
create_iu_dataset('data/example.xlsx')
print(iu)
```

## Compare the measurement and synthetic data

```{r compare}
data(iu)
IU <- iu[iu$Voltage>0,]
IU["Value"] = IU["Value"]/max(IU["Value"])
plot(IU, col='blue')
points(characteristic$voltage , characteristic$current, col='red')
legend('bottomright',inset=0.05,c("Model","Measurement"),lty=1,col=c("red","blue"),title="f(u)")

```

